---
title: "R Notebook"
output: html_notebook
---


Obtaining data from a source

```{r}
Data <- read.csv("D:/ALDA 2021/CRYSTAL System-Data Science project/Crystal-DS Project 3/TEC-DS -Week materials/Week 3/Data.csv")
head(Data)
Info.by.state <- read.csv("D:/ALDA 2021/CRYSTAL System-Data Science project/Crystal-DS Project 3/TEC-DS -Week materials/Week 3/Info by state.csv")
head(Info.by.state)
```

Q1: create a new dataset where these information is displayed 
```{r}
New_data<-dplyr::full_join(Data,Info.by.state,by="Country")
head(New_data)
View(New_data)
```

The function is not working because we have missing values which are removing observations and by this way making less observations.
So we need to deal with missing values NA.
```{r}
library(ggplot2)
GGally::ggpairs(New_data,mapping = aes(color = Country),na.omit=TRUE)
```

```{r}
which(is.na(New_data$Age))# will display positions of NA in Age variable
```
```{r}
# let fill these NA with the average age
# first we will create an index vector 
Ind_1<-which(is.na(New_data$Age))

# then we will substitute NA-s with teh average of the Age variable
New_data$Age[Ind_1]=mean(New_data$Age)
New_data$Age[Ind_1]
```
Q:What is happening?
A: some functions such as the mean () are not performing if there are missing observations. So we need to add the argument na.rm=TRUE

```{r}
New_data$Age[Ind_1]=mean(New_data$Age,na.rm = TRUE)
New_data$Age[Ind_1]
```
The same we will do for the other variables when we have missing values.

```{r}
Ind_2<-which(is.na(New_data$Salary))
# then we will substitute NA-s with the average of the Salary variable
Ind_2
```

```{r}
New_data$Age[Ind_2]=mean(New_data$Salary,na.rm = TRUE)
New_data$Age[Ind_2]
```

```{r}
Ind_3<-which(is.na(New_data$Purchased))
# then we will substitute NA-s with the mode of the Purchased variable
Ind_3
```


Another way of showing missing values NA in all variables of teh matrix:
```{r}
# apply(is.na(New_data), 2, which)
```

Unfortunately the function here is not working because of the small number of observation
```{r}
GGally::ggpairs(New_data,mapping = aes(color=Country))
GGally::ggpairs(New_data[,c(2,3)],mapping = aes(color=Purchased))

```

```{r}
GGally::ggpairs(New_data)
```

Q:Use information for states : Italy and Greece. Obtain some results

Extract information for Italy and Greece:

```{r}
library(dplyr)
Data_2<-New_data %>% filter(Country==c("Italy","Greece"))
Data_2
```

Q:Create a new dataset only for states Italy and Greece for individual observations (do
not display state information such as life expectancy, gdp, population)

```{r}
Data_3<- Data_2 %>% select (Country,Age, Salary, Purchased)
Data_3
```

